Naming of menus is a bit weird
Column sort not obvious
===
Outline what the site is on homepage
If no search term, say that + clear it
perhaps mention what is meant by a valid email address
While uploading a file, there should be a progress bar or something: mouse circle/OS 'wait' pointer is not noticeable enough
Make the clickable table headers more obvious
Say that items can be restored by choosing one
Show creation time on the display pages
Fields: Number and year - do they need int values or not?
In list all entries page, perhaps add a creation date column
empty fields are still showing up in downloaded file
not enough information given about exceptions
===
Cite key unique update or auto-assign citekey
Amend link
Personal note reminder about
how old are entries when they are purged?
click to upload - grey out until file selected in file selector - it is not clear that you have to choose a file first before pressing upload.
Click on an author to find all items by that author?
downoad specific chunk of database, e.g. search results.
specific ordering in file
Should name the page `View Entries' rather than `active'
search isn't a view - use a seperate entry or have a search box on the page
page after undelete shows no confirmation that it worked.
there should be a message that the entry has been deleted on the list of deleted entries.
cycle through all duplicates/have a list of all duplicates for one cite key - you might have 3 matches and the first two show up different, you'll not know that the 3rd is the one that is the exact copy that you want to delete
Issues with required fields
Need a page designed to view instead of just amend
===
List/Index page: tooltips over fields would make it easier to remember what each column is, though it might get annoying and you'd remember after getting used to it
Search not obvious - difficult to know where to look for search
a search for 'Article' does not return all articles
advanced search, date range, regex etc.?
instant search sometimes has overlap
highlighting of where it found the search term
undelete entry should be restore entry, hard to read
space the 'purge old' and 'purge all' commands further apart - could slip and delete the wrong one
categorisation of entries:tagging/allocation
want to see who is working on an entry and who added it
amend entry link in review duplicates
multiple duplicate entries - there should be a message to say so!
copy an entry from a url
don't know that you can sort tables
too many clicks when deleting an entry
restore entry should redirect to deleted entries page
not enough feedback to say that an entry has been deleted
export some entries, not all
stay on same page, review dups in one page
add entry - own button at top: "Edit" obscures that add is available
Create entry button not amend
Not clear how to separate authors - message to say how to separate
exception when year not provided
highlight what you've just added?
table overlaps end of page - can't see end of it.
'view' rather than amend -  want to be able to take raw bibtex format
add entry should have paste-in box like upload
parser rejected entry and didn't say why or that it was lost (not enough feedback from import
use quotes for each field, rather than braces?